The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2022-02-01 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd
Explaining why reviewer 1 suggestion of testing individual teams home court advantage was not possible given the available data size

Future studies may want to use the 2020 NBA bubble and compare vs previous years
using other performance measures. For example, turnovers, steals, assist, rebounds,
and many more game statistics. There are plenty of other possibilities besides
just shooting efficiency to pick through looking for more possible sources of
added points for away teams. This will further help explain what is lost in the
performance of away teams when they travel to opposing arenas. This study is only
the beginning of possibilities for studies using the 2020 NBA bubble as a case study
for home-court advantage. Although the study is limited by a one time
sample, it seems unlikely that these conditions will ever be
repeated. It may not be possible to have a follow-up study using the
same measures with a different sample. Otherwise, that type of study
could help strengthen the conclusion in this paper.

>>>>

Future studies may want to use the 2020 NBA bubble and compare vs previous years
using other performance measures. For example, turnovers, steals, assist, rebounds,
and many more game statistics. There are plenty of other possibilities besides
just shooting efficiency to pick through looking for more possible sources of
added points for away teams. This will further help explain what is lost in the
performance of away teams when they travel to opposing arenas. This study is only
the beginning of possibilities for studies using the 2020 NBA bubble as a case study
for home-court advantage. Although the study is limited by a one time
sample, it seems unlikely that these conditions will ever be
repeated. It may not be possible to have a follow-up study using the
same measures with a different sample. Otherwise, that type of study
could help strengthen the conclusion in this paper. Also, you could
answer more questions with a larger sample size. For example,  testing
strength of home court advantage relative to specific teams, like the
Denver Nuggets and Utah Jazz who we know from other literature may
have a stronger home court advantage. The sample size of home games
for the individual teams in the bubble was far too small to try and
address this question, the Jazz and Nuggets only had 3 and 9 home
games, respectively.
